---
title: "Programming Background"
author: "Simon Weisenhorn"
date: "2023-06-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path = "../images/")
```

## My Opinions and Experience with R

  In my programming experiences, I have coded with R, SAS, html/css, Typescript,
and very minimal amounts of Python. My opinion on R vs some of the other 
programming languages is that it is very simple and easy to use. I find it to be
very intuitive and straightforward, while also being advanced enough to conduct
interesting analyses and create fascinating outputs. This is in contrast to SAS
(my other most used programming language) which is usually not intuitive and 
harder to complete tasks that I am interested in achieving. SAS is also far less
popular, which leads to a lower amount of support online.  
  The functionality that I like most about R is how it is object oriented, which
makes working on projects far easier to comprehend because of how R stores 
information. This is much easier than dealing with how SAS treats information
in an action oriented format. However, I do miss the robust SAS documentation
page. The documentation of every function and procedure made it very easy to 
learn everything about how to achieve a desired output in a uniform way. R
certainly has a great community to learn from, but they aren't always super 
clear and sometimes show ways of doing things that are completely different from
someone else's approach.  
  Personally, I do not find R to be a difficult language to learn. I first 
learned it in my undergraduate courses and I think the object oriented format
makes it one of the less complicated languages. It can certainly be frustrating
to wrap your head around how a computer processes information and applies
function to different variables, but once I picked that up, things between
myself and R have gone fairly smoothly. I am super fortunate to know R at the 
level that I do now and I look forward to learning more this summer!

## Example R Markdown Output

```{r iris}
plot(iris)
```
