---
title: "Most Interesting Machine Learning Method"
author: "Simon Weisenhorn"
date: "2023-07-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I gained a lot of very helpful knowledge following the exploration we had with 
machine learning in this course. The machine learning method that I found most 
interesting was boosted trees. A boosted tree is a ensemble based model that 
treats the errors created by previous decision trees. By considering the errors 
of trees in previous rounds, the boosted tree model forms new trees sequentially 
where each tree is dependent on the previous tree. This adjustment accounts for 
overfitting which is one of the major drawbacks of regular decision trees. These 
kinds of models are also useful for non-linear data, which make them great for 
real world applications. Let’s explore a situation where a boosting tree might 
be helpful below.

### Set Up

```{r}
library(tidyverse)
library(datasets)
library(caret)
#loading the necessary libraries for the code below

Titanic <- data.frame(Titanic) #converting Titanic data to data frame
Titanic <- uncount(Titanic, weights=Freq) 
#duplicating rows based on weighted variable (Freq)

set.seed(558) #setting seed for reproducibility 

trainIndex <- createDataPartition(Titanic$Survived, p = 0.75, 
                                  list = FALSE)
#Creating indexes for training data 

TitanicTrain <- Titanic[trainIndex, ] #Creating training dataset
TitanicTest <- Titanic[-trainIndex, ] #Creating testing dataset
```

In the chunk above, I loaded in the data and partitioned it into a 75/25 
training testing split. The data consists of information about the Titanic 
passengers, such as their class, age, and gender, as well as whether they 
survived the wreck or not. The analysis below will utilize the variables in a
boosted tree model to predict whether a passenger survived.

### Boosted Tree

```{r message=FALSE}
library(gbm) #Need this library to run the training function

allTuningParameters <- expand.grid(n.trees=c(25,50,100,150,200), interaction.depth=c(1,2,3,4), shrinkage=0.1, n.minobsinnode = 10)
#Creating dataframe for the tuneGrid arguement using expand.grid

boostTreeFit <- train(Survived ~ ., data = TitanicTrain,
                      method = "gbm",
                      preProcess = c("center", "scale"),
                      trControl = trainControl(method = "repeatedcv", 
                                               number = 5, repeats=3),
                      tuneGrid=allTuningParameters,
                      verbose=FALSE)
#Fitting the boosted tree model

boostTreeFit
#viewing the resulting model
```

The chunk above was used to fit the boosted tree model, which uses 5 fold
repeated cross validation.

```{r}
confusionMatrix(data = TitanicTest$Survived, 
                reference = predict(boostTreeFit, newdata = TitanicTest))
#checking how well the model does on the test set using the confusionMatrix 
#function
```

Finally, in the last chunk, I used the confusionMatrix function to check how 
well the model did on the test set. The accuracy was 77.78% so not too bad 
overall, but it could certainly improve. The best way to explore further 
improvement would be to fit different ensemble models or adding additional
tuning parameters.

Overall, the boosted tree method is a very interesting machine learning method
and I look forward to exploring where I can utilize methods like this one in
future projects!
